Structured Versus Decorated Cospans

### 2020-12-11 cospans.tex
tried to fix Lemma 3.4 - check it!

% Structured versus decorated cospans
% John Baez, Kenny Courser and Christina Vasilakopoulou
% in LaTeX
% 2020/12/9

@@

\begin{lem}[\textbf{Hermida}] \label{lem:fibrewiselimits}
Suppose $\J$ is a small category and $U\maps\X\to\A$ is an opfibration. If the base $\A$ has $\J$-colimits,
the following are equivalent:
\begin{enumerate}
 \item all fibers have $\J$-colimits, and the reindexing functors preserve them;
 \item the total category $\X$ has $\J$-colimits, and $U$ preserves them.
\end{enumerate}
Given these conditions, for any choice of $\J$-colimits in $\A$ the $\J$-colimits in $\X$ can be chosen so that $U$ strictly preserves them.   NEEDS FIXING!!!  %%%!!!
\end{lem}

>>>>

% Structured versus decorated cospans
% John Baez, Kenny Courser and Christina Vasilakopoulou
% in LaTeX
% 2020/12/10

@@

SEE IF THIS IS RIGHT:  %%%!!!
\begin{lem}[\textbf{Hermida}] \label{lem:fibrewiselimits}
Suppose $\J$ is a small category and $U \maps \X \to \A$ is an opfibration where the base 
$\A$ has $\J$-colimits.  Then the following are equivalent:
\begin{enumerate}
 \item all fibers have $\J$-colimits, and the reindexing functors strictly preserve them;
 \item the total category $\X$ has $\J$-colimits and $U$ strictly preserves them.
\end{enumerate}
Moreover, if $\X$ has $\J$-colimits and $U$ preserves them, they can be chosen so that $U$ strictly preserves them.   
\end{lem}
